Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-13 automatica/paper.tex
revised intro

Modern implementations of embedded control systems have proliferated
with the availability of low-cost devices that can perform highly
non-trivial control tasks, with significant impact in numerous
application areas such as life sciences, environmental control and
robotics~\cite{astrom1997computer, Franklin15}.  Correct synthesis of
control software for such platforms is non-trivial, even in cases with
restriceted dynamics.  We examine the case of Linear Time Invariant
(LTI) models, for which the synthesis of controllers is well
understood.  However, the use of digital control architectures adds
new challenges caused by artifacts specific to digital control, such
as the effects of finite-precision arithmetic, time discretization and
quantization noise introduced by A/D and D/A conversion.

In this paper we develop an automatic technique for generating digital
controllers for a given continuous plant model that are correct by
construction.  Specifically, we synthesize stable and safe,
software-implemented embedded controllers.  Due to the complexity of
such closed-loop systems, we focus on linear models with known
configurations, and perform parametric synthesis of controllers
meeting a number of properties that define their desired behavior.

@@

Our work addresses challenging aspects of the control synthesis problem.  We
perform digital control synthesis over a hybrid model, where the plant
exhibits continuous behavior whereas the controller operates in discrete
time and over a quantized domain.  In particular, our model evaluates the
effects of the quantizers (A/D and D/A converters) and of time
discretization, as well as representation errors introduced by in modelling
artifacts such as an observer~\cite{astrom1997computer} in a finite
precision domain, while reasoning about high level properties such as
stability, robustness, and safety, which define the behaviour
of the system.  In particular, safety requirements are frequently overlooked
in conventional feedback control synthesis, but play an important role in
systems engineering.

@@

%% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17}
and makes the following contributions, where the fourth and he fifth denote
extensions over \cite{DBLP:conf/cav/AbateBCCDKKP17}.
%
\begin{enumerate}

>>>>

Modern implementations of embedded control systems have proliferated
with the availability of low-cost devices that can perform highly
non-trivial control tasks, with significant impact in numerous
application areas such as life sciences, environmental control and
robotics~\cite{astrom1997computer, Franklin15}.  Correct synthesis of
control software for such platforms is non-trivial, even in cases with
restricted dynamics.

In this paper, we examine the case of Linear Time Invariant (LTI)
models, for which the synthesis of controllers is well understood.
However, the use of digital control architectures adds new challenges
caused by artifacts specific to digital control, such as the effects
of finite-precision arithmetic, time discretization and quantization
noise introduced by A/D and D/A conversion.
%
Given an LTI model, we develop an automatic technique for generating
correct by construction digital controllers that addresses all these
challenges. Specifically, we synthesize stable and safe,
software-implemented embedded controllers.  Due to the complexity of
such closed-loop systems, we focus on linear models with known
configurations, and perform parametric synthesis of controllers.
%meeting a number of properties that define their desired behavior.

@@

Our work addresses challenging aspects of the control synthesis
problem.  We perform digital control synthesis over a hybrid model,
where the plant exhibits continuous behavior whereas the controller
operates in discrete time and over a quantized domain.  In particular,
our model evaluates the effects of the quantizers (A/D and D/A
converters) and of time discretization, as well as representation
errors introduced by modeling %% artifacts such as an
%% observer~\cite{astrom1997computer}
in a finite precision domain, while reasoning about high level
properties such as stability, robustness, and safety, which define the
behaviour of the system.  Notably, safety requirements are
frequently overlooked in conventional feedback control synthesis, but
play an important role in systems engineering.

@@

%% \addtodo{CD: the novelty compared to CAV'17 needs to be clarified}
This paper represents an extension of \cite{DBLP:conf/cav/AbateBCCDKKP17}
and makes the following contributions, where the fourth and the fifth denote
extensions over \cite{DBLP:conf/cav/AbateBCCDKKP17}.
%
\begin{enumerate}
